Report for the Deep Learning Course Assignment 3

### 2016-12-16 practical_3/report/report_methenitis.tex
final submission

\subsubsection{Dropout}

@@

classif = OneVsRestClassifier(SVC(kernel='linear'))
classif.fit(features[train_set], batch_y[train_set]
classif.score(features[test_set], batch_y[test_set]
\end{verbatim}
Here, the reported accuracy\footnote{The accuracy is reported to half of the test set ($5000$ random samples without replacement due to slow training of the OneVsRestClassifier		)} of the one-vs-classifiers on the test set:
\begin{itemize}
\item Accuracy with flatten features: $0.6305$.
\item Accuracy with fc1 features: $0.59$.
\item Accuracy with fc2 features: $\mathbf{0.7685}$.
\end{itemize}
It is natural that the accuracy is higher for later layers.
As it was earlier $fc2$ layer can distinguish better features of different classes.

@@

In the previous section I set up three experiments and presented the loss during training in the training set.
In this section I illustrate the features in the 2-dimensional space as these transformed by TSNE (as this was implemented in Section~\ref{sec:vis}.).

@@

In this section I present the results of my implementation for the feature extraction of the third task.
I used the last 3 layers of the convNet inference method from the first task of the assignment.
I also used stopGradient method of tensorflow to disconnect vgg pretrained network from convNet and the training updates.

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-transfer.png}\	
\includegraphics[width=12.2cm]{loss-transfer.png}
\caption{}
\label{fig:extra}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-retrain.png}\	
\includegraphics[width=12.2cm]{loss-retrain.png}
\caption{}
\label{fig:retrain}
\end{figure}

@@

\subsection{Performance of transfer learning on Cifar10}
\begin{description}
\item[Feature extraction:]{$0.6743$}
\item[Retraining:]{$0.8505$}
\item[Refining-$100$:]{$0.8441$}
\item[Refining-$1000$:]{$0.8461$}
\item[Refining-$2500$:]{$\mathbf{0.8510}$}
\end{description}

>>>>

\subsubsection{Dropout}
Figure~\ref{fig:6} illustrates the results with dropout enables for values $0.2, 0.5$.

@@

classif = OneVsRestClassifier(SVC(kernel='linear'))
classif.fit(features[train_set], batch_y[train_set]
classif.score(features[test_set], batch_y[test_set]
\end{verbatim}
Here, the reported accuracy of the one-vs-classifiers on the test set:
\begin{itemize}
\item Accuracy with flatten features: $0.6305$.
\item Accuracy with fc1 features: $0.7465$.
\item Accuracy with fc2 features: $\mathbf{0.7685}$.
\end{itemize}
It is natural that the accuracy is higher for later layers.
As it was earlier shown $fc2$ layer can generates features that the one-cs-rest classifier can distinguish different classes easier than from the other layers.

@@

In the previous section I set up three experiments and presented the loss during training in the training set.
In this section I illustrate the features in the 2-dimensional space as these transformed by TSNE (as this was implemented in Section~\ref{sec:vis}).
Figure~\ref{fig:features} presents the features generated by the normalized output layer of the network for the setting used in the 3 experiments.

@@

In this section I present the results of my implementation for the feature extraction of the third task.
I used the last 3 layers of the convNet inference method from the first task of the assignment.
I also used stopGradient method of tensorflow to disconnect vgg pretrained network from convNet and the training updates.
Figure~\ref{fig:extra} illustrates the performance on the training and the test set for $10000$ training steps.
The accuracy, when updating only the last three layers of the network, approximates $0.67$ which is lower than the performance of the network in task 1.
It shows that features obtained by another pretrained network cannot work that well in an another task.

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-transfer.png}\	
\includegraphics[width=12.2cm]{loss-transfer.png}
\caption{(Feature extraction) Accuracy and loss in the training (purple line) and the test set (yellow line) for $10000$ training step.}
\label{fig:extra}
\end{figure}

@@

Here I present the results of retraining, stop gradient is disabled and thus all the weights are updated from the beginning of the training procedure.
Figure~\ref{fig:retrain} illustrates the performance on the training and the test set for $10000$ training steps.
The accuracy approximates $0.85$ which is $9\%$ higher than the best performance achieved in task 1 of the assignment.
Which is a natural result given that weights are initialized with ``good'' priors.

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-retrain.png}\	
\includegraphics[width=12.2cm]{loss-retrain.png}
\caption{(Retraining) Accuracy and loss in the training (orange line) and the test set (brown line) for $10000$ training step.}
\label{fig:retrain}
\end{figure}

@@

Here I present the results of refining, stop gradient is disabled after $k$-training steps and thus all the weights are updated only after $k$-step during training.
Figure~\ref{fig:refine} illustrates the performance on the training and the test set for $10000$ training steps.
The accuracy approximates $0.85$ which is equivalent to the performance achieved in the retraining task.
Note, the big drops in accuracy and jumps in loss after the refining starting step.
This is due to the heavy influence the initial layers of the VGG have on the classification, where small changes in the weights influence a lot the output of the network.

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-refine.png}\	
\includegraphics[width=12.2cm]{loss-refine.png}
\caption{(Refining) Accuracy and loss in the training (orange line) and the test set (blue line) for $10000$ training step, refining after $100$ training steps.
Accuracy and loss in the training (purple line) and the test set (cyan line) for $10000$ training step, refining after $1000$ training steps.
Accuracy and loss in the training (green line) and the test set (blue line) for $10000$ training step, refining after $2500$ training steps.}
\label{fig:refine}
\end{figure}

\subsection{Performance of transfer learning on Cifar10}

Here I present the results on the test set after $10000$ training steps of all the methods studied above.
\begin{description}
\item[Feature extraction:]{$0.6743$}
\item[Retraining:]{$0.8505$}
\item[Refining-$100$:]{$0.8441$}
\item[Refining-$1000$:]{$0.8461$}
\item[Refining-$2500$:]{$\mathbf{0.8510}$}
\end{description}
The highest performance was achieved by refining-$2500$ where the weights of the pre-trained network started to be optimized for the Cifar10 task after $2500$ training steps.
However, the performance was approximately equivalent to the retraining method, where all weights are updated during the whole period of training.
